When Do You Repeat Yourself?\\ Voices from the Trenches of Linux Kernel Maintainers on Code Duplication

### 2025-10-29 papers/techdebt2026/techdebt.tex
techdebt2026: techdebt: make DRY highlight box unique
The highlight box of the DRY principle on the introduction was of the
same color as the takeaway boxes. To differentiate, make it blue-ish.

Signed-off-by: David Tadokoro <davidbtadokoro@usp.br>

\documentclass[10pt,conference]{IEEEtran}
\usepackage{graphicx,url}
\usepackage{hyperref}
\usepackage{nicematrix}
\usepackage{array}
\usepackage[utf8]{inputenc}  
\usepackage{seqsplit}
\usepackage{todonotes}

%% Takeaway Boxes %%
\usepackage[most]{tcolorbox}
\tcbset{colback=gray!10, colframe=gray!50!black, boxrule=0.5pt,
        left=1mm, right=1mm, top=1mm, bottom=1mm, sharp corners}

\newenvironment{highlight-box}[1]{%
  \begin{tcolorbox}
  \textbf{#1:} \itshape}{\end{tcolorbox}}
%% Takeaway Boxes %%

@@

\begin{highlight-box}{DRY principle}
  ``We feel that the only way to develop software reliably, and to make our
  developments easier to understand and maintain, is to follow what we call the
  DRY principle: Every piece of knowledge must have a single, unambiguous,
  authoritative representation within a system''.
\end{highlight-box}

>>>>

\documentclass[10pt,conference]{IEEEtran}
\usepackage{graphicx,url}
\usepackage{hyperref}
\usepackage{nicematrix}
\usepackage{array}
\usepackage[utf8]{inputenc}  
\usepackage{seqsplit}
\usepackage{todonotes}
\usepackage[most]{tcolorbox}

%% Takeaway Boxes %%
\newenvironment{highlight-box}[1]{%
  \begin{tcolorbox}[colback=gray!10, colframe=gray!50!black, boxrule=0.5pt,
                    left=1mm, right=1mm, top=1mm, bottom=1mm, sharp corners]
  \textbf{#1:} \itshape}{\end{tcolorbox}}
%% Takeaway Boxes %%

%% DRY Highlight Box %%
\newenvironment{dry-highlight-box}[1]{%
  \begin{tcolorbox}[colback=blue!5!white, colframe=blue!60!black, boxrule=0.5pt,
                    left=1mm, right=1mm, top=1mm, bottom=1mm, sharp corners]
  \textbf{#1:} \itshape}{\end{tcolorbox}}
%% DRY Highlight Box %%

@@

\begin{dry-highlight-box}{DRY principle}
  ``We feel that the only way to develop software reliably, and to make our
  developments easier to understand and maintain, is to follow what we call the
  DRY principle: Every piece of knowledge must have a single, unambiguous,
  authoritative representation within a system''.
\end{dry-highlight-box}
